The Civil Society Organizations effect: A mixed-Methods analysis of bottom-up approaches in Brazilian public policy

### 2023-11-06 Scripts/paper.Rmd
paper versão anterior

---
title: "The Civil Society Organizations effect: A mixed-Methods analysis of bottom-up approaches in Brazilian public policy"
date: "2023-10-26"
output: bookdown::pdf_document2
sansfont: Sans Serif
fontsize: 12pt
author:
  - name: Manoel Galdino
    affiliation: Universidade de São Paulo - Brazil.
  - names: Juliana Sakai
    affiliation: Transparência Brasil - Brazil
  - names: Bianca Vaz Mondo
    affiliation: Transparência Brasil - Brazil
  - names: Natália Paiva
    affiliation: Alandar Consulting - Brazil
abstract: "This paper examines the effect of bottom-up accountability on public service delivery. We differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs), and argue that the latter type of interventions can can drive significant policy change. The study evaluates the effectiveness of the Obra Transparente project by Brazilian NGO Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil.  Our findings emphasize the importance of sustained, coordinated efforts by socially embedded CSOS. These efforts, involving direct engagement with municipal officials and ensuring that their complains cannot be ignored lead to more substantial outcomes when compared with citizens information-driven."
keywords: "accountability, Civil Society Organizations, mixed methods, community-driven development, public policy."
bibliography: OT_paper.bib
---

>>>>

---
title: "The Civil Society Organizations effect: A mixed-Methods analysis of bottom-up approaches in Brazilian public policy"
date: "2023-10-26"
sansfont: Sans Serif
fontsize: 12pt
author:
- name: Manoel Galdino^[Universidade de São Paulo - Brazil, mgaldino@usp.br]
- names: Juliana Sakai^[Transparência Brasil - Brazil]
- names: Bianca Vaz Mondo^[Government Transparency Institute - Germany]
- names: Natália Paiva^[Alandar Consulting - Brazil]

abstract: "This paper examines the effect of bottom-up accountability on public service delivery. We differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs), and argue that the latter type of interventions can can drive significant policy change. The study evaluates the effectiveness of the Obra Transparente project by Brazilian NGO Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil.  Our findings emphasize the importance of sustained, coordinated efforts by socially embedded CSOS. These efforts, involving direct engagement with municipal officials and ensuring that their complains cannot be ignored lead to more substantial outcomes when compared with citizens information-driven."
keywords: "accountability, Civil Society Organizations, mixed methods, community-driven development, public policy."
bibliography: OT_paper.bib
output:
    bookdown::pdf_document2:
      base_format: rticles::sage_article

---
